Quantifying Stability and Change in Personal Culture Using Panel Data

### 2023-09-24 manuscript.Rmd
integrated aggregate change into implications for cultural sociology.

## Implications for Social Change

Because intrapersonal change in personal culture does not appear to be a driving force in cultural differences among adults, our results suggest that processes of social and cultural change at the aggregate level are likely driven more by cohort replacement, one group of people with certain cultural dispositions exiting the population and a different set of people with a potentially different set of cultural dispositions entering the population, than by contemporaneous social conditions [@vaisey2016; @underwood2022]. This is likely true for both large-scale change in societies over time as well as changes within organizations, political parties, occupations, and other social aggregates.

However, because our results suggest that the role of formative experiences compared to contemporaneous environments differs by a person's level of education, changes in educational attainment over time, as well as changes in the social structuring of the life course might be shifting the relative importance of these two factors over time. If we observe further differences across socio-demographic groups like education, social class, and race/ethnicity in the relative importance of these processes, this would argue for a greater incorporation of the interaction of demographic processes with processes of individual cultural change into our explanations of aggregate cultural change.

>>>>

Our findings also have implications for understanding cultural change at the aggregate level. Given that intrapersonal change does not appear as the primary driver for cultural differences among adults, our results suggest that cultural change at the aggregate level is more likely driven by processes of cohort replacement than by contemporaneous social conditions influencing a given cohort's cultural dispositions [@vaisey2016; @underwood2022]. This likely holds true for cultural change at the macro societal level as well as the micro level such as within organizations, political parties, and professions. At the same time our findings point to the fact that the importance of formative experiences versus contemporaneous social influence for cultural change hinges on individuals' level of education. The relative importance of these two factors might thus shift as education becomes more or less prominent at different points in the life course. Should scholars find similar differences across other social categorizations such as class or race, it would suggest to more strongly incorporate demographic processes into the analysis of change at the aggregate level.
